Draft - sGBJ

### 2024-12-16 reporting/master_draft/draft_sgbj.qmd
update report

```{r kmbreastcancer, fig.cap="Kaplan meier curves for Astro, Oligo"}
p_type <- survfit2(Surv(time=time, event=event) ~ grade,
               data = df_data) %>% 
  ggsurvfit(linewidth = 1.1) +
  add_confidence_interval() +
  add_risktable(risktable_stats = "n.risk") +
  scale_color_manual(values = c("#F48C06", "#DC2F02", "#9D0208")) +
  scale_fill_manual(values = c("#F48C06", "#DC2F02", "#9D0208")) +
  labs(fill = "Grade", color = "Grade", y ="Survival \n Probability")
```

>>>>

```{r kmbreastcancer, fig.cap="Kaplan meier curves for Astro, Oligo"}
p_type <- survfit2(Surv(time=time, event=event) ~ grade,
               data = df_data) %>% 
  ggsurvfit(linewidth = 1.1) +
  add_confidence_interval() +
  add_risktable(risktable_stats = "n.risk") +
  scale_color_manual(values = c("#F48C06", "#DC2F02", "#9D0208")) +
  scale_fill_manual(values = c("#F48C06", "#DC2F02", "#9D0208")) +
  labs(fill = "Grade", color = "Grade", y ="Metastasis free \n survival probability")
```
